### 2025-02-10 Manuscript.qmd
Add YAML

---
title: "Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality"
shorttitle: "Queer Media Characters and LGBTQ+ Well-Being"
author:
  - name: Dingning Yang
    corresponding: true
    orcid: 0009-0008-5546-962X
    email: dingningy@uchicago.edu
    affiliations:
      - name: University of Chicago
        department: Department of Social Sciences
        address: 5105 South Harper Ave.
        city: Chicago
        region: IL
        country: USA
        postal-code: 60615-4156
author-note:
  status-changes: 
    affiliation-change: ~
    deceased: ~
  disclosures:
    study-registration: ~
    data-sharing: ~
    related-report: ~
    conflict-of-interest: ~
    financial-support: ~
    gratitude: ~
    authorship-agreements: ~
abstract: |

  | The growing visibility of the LGBTQ+ community is accompanied by the flourishing of queer characters in media in the information era. While previous studies have explored the double-edged impact of queer media representation on LGBTQ+ individuals’ development, few have compared these effects across different LGBTQ+ subgroups. This study investigates queer media characters’ psychological impacts on LGBTQ+ individuals with different identities, examining the relationship between perceived character authenticity, intersectionality, and characters’ impacts on LGBTQ+ individuals’ psychological well-being using a reliable survey instrument in a worldwide sample.

  | Findings revealed that marginal groups within the LGBTQ+ community, including those from developing countries, gender minorities, and racial minorities, reported higher scores about queer media characters’ positive impacts on psychological well-being compared to their mainstream counterparts. However, in terms of sexual orientation, mainstream groups (i.e., gay and lesbian respondents) showed higher scores. Importantly, the study found strong positive correlations between authenticity ratings, intersectionality ratings, and scores of queer characters’ positive impacts on psychological well-being.

  | This study contributes to a more nuanced understanding of LGBTQ+ individuals' diverse needs and experiences with queer media representation, which has significant implications for media producers, mental health professionals, and LGBTQ+ advocacy groups in fostering more positive and inclusive media representations for the LGBTQ+ community.
keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
bibliography: References.bib
format:
  apaquarto-pdf:
    documentmode: man
    indent: true
    include-in-header: 
      text: |
        \usepackage{setspace}
        \linespread{2}
---

# Method

## Participants

## Measures

## Procedure

# Results

# Discussion

## Limitations and Future Directions

## Conclusion

# References

<!-- References will auto-populate in the refs div below -->

::: {#refs}
:::

# Appendix

# Title for Appendix

### 2025-02-10 Manuscript.qmd
Update intro paragraph

@@
 keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
-bibliography: References.bib
 format:
   apaquarto-pdf:
+    csl: apa.csl
     documentmode: man
@@
         \linespread{2}
+bibliography: References.bib
 ---
+Since the Stonewall riots, queer characters have flourished in the mass media, reaching their peak in the information era.
+As the primary audience for queer media characters, the LGBTQ+ community is claimed to be both positively and negatively impacted by these characters [e.g., @craig_media:_2015;@nolke_making_2018].
+While queer characters can help LGBTQ+ individuals’ self-identity development and enhance their self-esteem, stereotypical representations that lack intersectionality may result in stigmatization and negative mental outcomes.
+Nevertheless, few studies have compared queer characters’ impacts on different sexual orientation or gender identity groups, probably because they ignored the emergence of more marginal groups (e.g., asexual).
+Additionally, no established instruments have explored how the differences in LGBTQ+ individuals’ queer media consumption, perceived character authenticity, or perceived intersectionality may contribute to different psychological well-being outcomes.
+Knowing different LGBTQ+ groups’ perceptions of queer media characters is essential to achieving internal equality within the LGBTQ+ community.
+Through developing a reliable and validated instrument on queer media characters’ psychological impacts and conducting worldwide data collection across different LGBTQ+ generations, this study aimed to contribute to a deeper understanding of queer characters’ psychological impacts on different LGBTQ+ groups, which can ultimately support the media industry to provide more diversified and inclusive queer representations.
 

### 2025-02-10 Manuscript.qmd
Update intro paragraph

--- 2025-02-10 Manuscript.qmd
@@
         \linespread{2}
+bibliography: References.bib
 ---
+Since the Stonewall riots, queer characters have flourished in the mass media, reaching their peak in the information era.
+As the primary audience for queer media characters, the LGBTQ+ community is claimed to be both positively and negatively impacted by these characters [e.g., @craig_media:_2015;@nolke_making_2018].
+While queer characters can favorably impact LGBTQ+ individuals’ identity development and self-esteem, stereotypical representations that lack intersectionality may result in stigmatization and negative mental outcomes.
+Nevertheless, few studies have compared queer characters’ impacts on different LGBTQ+ subgroups, probably because they ignored the emergence of more marginal groups (e.g., asexual).
+Additionally, no established instruments have explored how perceived character authenticity or intersectionality may contribute to different psychological well-being outcomes.
+Knowing LGBTQ+ individuals' diverse needs and experiences with queer media representation is important as it can call for more diverse and inclusive queer media representations.
+Through developing a reliable instrument on queer media characters’ psychological impacts and conducting worldwide data collection across different LGBTQ+ generations, this study aimed to contribute to a deeper understanding of queer characters’ psychological impacts on different LGBTQ+ groups.
+
+# Literature Review
+
+##
 

### 2025-02-10 Manuscript.qmd
Update lit review

@@
         \linespread{2}
+        \renewcommand{\footnotesize}{\fontsize{8}{10}\selectfont}
 bibliography: References.bib
@@
 
-##
+## LGBTQ+ Community and Queer Media Characters
+
+@IpsosLimited2024 has found that 17% of Generation Zers^[Generation Z (born between 1996-2012), Millennials (born between 1980-1995), Generation X (born between 1966-1979) and Baby Boomers (born between 1945-1965).] identified as part of the LGBTQ+ community, including identities such as lesbian, gay, bisexual, transgender, queer, asexual, and non-binary.
+This indicates a significant increase compared with prior generations, with only 11% for Millennials, 6% for Generation Xers, and 5% for Baby Boomers.
+The evolution within the LGBTQ+ community is accompanied by the flourishing of queer characters in TV shows and films that cater to their needs for identity affirmation and psychological belonging.
+For instance, the past ten years have witnessed a more than 300% increase in the number of LGBTQ+ characters on broadcast [@GLAAD2024].
+Compared with earlier queer characters that often feature heavy stereotypes (e.g., Frank-N-Furter in *Rocky Horror*), queer characters nowadays feature more multidimensional personalities and diversity, indicating progress in the representation of queer lives in media.
+
+## Queer Media Characters’ Positive Impacts on the LGBTQ+ Community
+
+@toomey_coping_2018 indicated that LGBTQ+ individuals may rely on social and cultural resources to enhance identity affirmation and cope with stress.
+Prior studies found that queer media characters can positively affect LGBTQ+ individuals as an effective coping strategy.
+@gomillion_influence_2011 conducted surveys and interviews on lesbian, gay, and bisexual (LGB) youth from Texas, suggesting that queer media characters, as role models, could positively affect LGB youth’s self-identity by enhancing their self-esteem and courage.
+While @gomillion_influence_2011 ignored transgenders and genderqueers, @craig_media:_2015 showed that queer media characters could help LGBTQ youth improve their self-assurance and build relationships with people having shared identities.
+Nevertheless, prior studies convergently focused on queer characters’ impacts on LGBTQ+ youth in the United States, ignoring cross-generation and cross-country comparisons, which may result in low external validity of the findings.
+Additionally, these studies barely compared different sexual orientations and gender identities in the LGBTQ+ community, which may neglect more marginalized groups’ perceptions and experiences (e.g., asexual and pansexual).
+
+## Queer Media Stereotypes’ Negative Impacts on the LGBTQ+ Community
+
+Some studies have also criticized that queer media characters presenting stereotypes could be harmful to the LGBTQ+ community.
+@yaksich_consuming_2005 and @guidotto_cashing_2006 indicated that many queer media representations are the commodification of the LGBTQ+ community.
+The queer media monopoly of ‘perfect homo’ (i.e., flamboyant Caucasian and middle-classed gay men) neglects intersectionality, reinforcing the LGBTQ+ stereotypes in the audience’s perceptions.
+@nolke_making_2018 identified the intersectional invisibility of queer media representations by applying intersectional analysis of a series of advertisements from 2009 to 2015.
+The discussion from this study also indicated that the hegemony of queer stereotypes and the lack of intersectionality could be harmful to the LGBTQ+ community by bringing them lower confidence and mental illnesses (e.g., depressive disorders).
 

### 2025-02-10 Manuscript.qmd
Update lit review
Update current study and hypo

@@
 The discussion from this study also indicated that the hegemony of queer stereotypes and the lack of intersectionality could be harmful to the LGBTQ+ community by bringing them lower confidence and mental illnesses (e.g., depressive disorders).
+Nevertheless, no established instrument has systematically compared how LGBTQ+ perceived queer character authenticity (i.e., free of stereotypes) or perceived queer character intersectionality could impact their psychological well-being, calling for more scholarly intention to relevant measurement.
+
+# Current Study and Hypotheses
+
+The current study examined queer media characters’ impacts on LGBTQ+ individuals’ psychological well-being through two overarching research questions.
+The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities.
+Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and nationalities on queer characters’ psychological impacts.
+Given the fact that there were still queer stereotypes and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents).
+The second research question asked whether queer media consumption patterns, perceived character authenticity, and perceived character intersectionality can predict queer media characters’ psychological impacts.
+Specifically, this study hypothesized that lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impacts.
+Conversely, higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impacts.
 

### 2025-02-10 Manuscript.qmd
Update method (before data analysis)

@@
 ## Participants
+This study recruited 180 LGBTQ+ participants worldwide through the data collection platform Prolific.
+Specifically, the respondents were aged from 18 to 72 in 17 countries (including countries in North America, Europe, Asia, and Africa) with different sexual orientations, gender identities, and racial identities, satisfying the research needs for comparisons among LGBTQ+ individuals with different identities on queer media characters’ psychological impacts.
+Each participant was paid $2 to participate in a survey with a seven-minute average finish time.
 
-## Measures
+## Measurements
 
-## Procedure
+This study developed a survey instrument on Qualtrics to explore queer media characters’ psychological impacts among different LGBTQ+ individuals with five sections:
+
+* ***Demographic form***: The demographic form includes nine questions that ask participants’ age, residential country (and state if living in the US), gender identity, sexual orientation, racial identity, and education levels.
+
+* ***Queer media consumption***: The queer media consumption scale asks five questions regarding participants’ exposure and engagement with queer media characters.
+Specifically, the scale measures the frequency of watching queer TV shows or movies, the discussion engagement of queer representations on social media, and the specific queer media genre and names as a mix of close-ended and open-ended questions.
+
+* ***Queer character authenticity***: The queer character authenticity scale consists of seven questions, with four of them asking the extent to which queer characters can reflect individual experiences in daily life.
+The other three questions measure the extent to which queer characters displaying stereotypes, which are reverse-coded.
+The sum of seven questions consists of the authenticity rating of the whole scale.
+
+* ***Queer character intersectionality***: The queer character intersectionality scale consists of four questions that ask the extent to which queer characters can reflect diverse experiences of multiple factors such as racial and socioeconomic backgrounds.
+
+* ***Queer character’s psychological impacts***: This scale measures queer characters’ impacts on participants’ psychological well-being, which is constituted of three sub-scales: 
+  + Self-development (seven questions)
+  + Community belonging (six questions)
+  + Emotional well-being (eight questions)
 

### 2025-02-11 Manuscript.qmd
Update data analysis

@@
 keywords: [LGBTQ+ well-being, queer media representations, intersectionality]
+floatsintext: true
 format:
@@
 ---
+
+```{r,include=FALSE}
+#| label: setup
+# Install required packages
+if(!require(tidyverse)){install.packages("tidyverse")}
+if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(psych)){install.packages("psych")}
+if(!require(knitr)){install.packages("knitr")}
+if(!require(kableExtra)){install.packages("kableExtra")}
+
+# List of required packages
+required_packages <- c ("tidyverse", "ggplot2", "psych","knitr", "kableExtra")
+
+# Load required packages
+lapply(required_packages, library, character.only = TRUE)
+set.seed(123)
+
+```
+
 Since the Stonewall riots, queer characters have flourished in the mass media, reaching their peak in the information era.
@@
 The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities.
-Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and nationalities on queer characters’ psychological impacts.
+Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and residential countries on queer characters’ psychological impacts.
 Given the fact that there were still queer stereotypes and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents).
@@
 
+## Data Analysis
+
+```{r,include=FALSE}
+#| label: read in cleaned and transformed datasets
+# Read in the cleaned and transformed dataset
+queer.cleaned <- read_csv("data/queer.cleaned.csv")
+queer.hypo <- read_csv("data/queer.hypo.csv")
+media.long <- read_csv("data/media.long.csv")
+
+```
+
+Data was preprocessed through RStudio and transformed into a tidy format for analysis.
+
+```{r,include=FALSE}
+#| label: Source data analysis script
+source("Source/Data Analysis.R")
+
+```
+
+### Reliability Tests
+Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (see Table 1).
+Cronbach's alpha coefficients were calculated for each scale.
+Specifically, the authenticity rating measurement demonstrated satisfactory reliability (α = 0.76).
+The intersectionality rating measurement showed excellent reliability (α = 0.91).
+Both the media individual development scale and the media community belonging scale exhibited excellent reliability (α = 0.96 for both).
+The emotional well-being measurement also demonstrated excellent reliability (α = 0.96).
+Finally, the overall psychological well-being measurement showed the highest reliability with an excellent Cronbach's alpha of 0.98.
+These results indicate that all scales used in this study have good to excellent internal consistency, suggesting they are reliable measures of their respective constructs.
+
+```{r}
+#| label: Generate reliability test tables
+#| echo: false
+#| warning: false
+#| message: false
+#| tbl-cap: "Reliability Analysis Results"
+
+reliability_kable <- data.frame(
+  Scale = c("Authenticity rating", 
+            "Intersectionality rating", 
+            "Queer media individual development impact", 
+            "Queer media community belonging impact", 
+            "Queer media Emotional well-being impact", 
+            "Queer media overall psychological well-being impact"),
+  Items = c("7", "4", "7", "6", "8", "21"),
+  Alpha = c(
+    psych::alpha(queer.construct[,20:26], check.keys=TRUE)$total$raw_alpha,
+    psych::alpha(queer.construct[,27:30])$total$raw_alpha,
+    psych::alpha(queer.construct[,31:37])$total$raw_alpha,
+    psych::alpha(queer.construct[,38:43])$total$raw_alpha,
+    psych::alpha(queer.construct[,44:51])$total$raw_alpha,
+    psych::alpha(queer.construct[,31:51])$total$raw_alpha
+  )
+)
+
+reliability_kable$Alpha <- round(reliability_kable$Alpha, 2)
+
+reliability_kable <- reliability_kable %>%
+  mutate(Interpretation = case_when(
+    Alpha < 0.60 ~ "Poor",
+    Alpha < 0.70 ~ "Questionable",
+    Alpha < 0.80 ~ "Acceptable",
+    Alpha < 0.90 ~ "Good",
+    Alpha >= 0.90 ~ "Excellent"
+  ))
+
+kable(reliability_kable, 
+      caption = "Reliability Tests Results",
+      col.names = c("Scale", "Number of Items", "Cronbach's alpha", "Interpretation"),
+      align = c("l", "c", "c", "c"),
+      booktabs = TRUE,
+      format = "latex") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = FALSE) %>%
+  column_spec(1, width = "5cm") %>%
+  column_spec(2, width = "2.5cm") %>%
+  column_spec(3, width = "2.5cm") %>%
+  column_spec(4, width = "2.5cm")
+
+```
+
+```{r, include=FALSE}
+#| label: Prepare for inline character display
+
+sexual_orientation_inline<- c("asexual","bisexual","gay or lesbian","pansexual","and queer")
+
+```
+
+### Respondent Characteristics
+167 respondents were eligible for the data analysis after data cleaning.
+Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old.
+The average age of the sample was `r round(mean(queer.hypo$age), 2)` years old (SD = `r round(sd_age, 2)`).
+This wide age range ensured the study captured perspectives from individuals across different generations.
+Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (see Fig 1), with both developed and developing country status, providing a global perspective.
+Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender.
+Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender.
+The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (see Fig 2).
+The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native.
+This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersecting identities.
+
+::: {#fig-residential layout-ncol=2}
+
+![Country Distribution](Image/Fig 01_Number of participants by country_bar.png){#fig-country}
+
+![Continent Distribution](Image/Fig 02_Number of participants by country_map.png){#fig-continent}
+
+Residential Distribution
+
+:::
+
+![Sexuality Distribution](Image/Fig 03_Gender identity_Transgender status_Sexual orientation_pie.png)
+
 # Results
+
+## Queer Media Characters’ Psychological Impacts on Different LGBTQ+ Subgroups
 

### 2025-02-11 Manuscript.qmd
Update results of hypo 1

@@
 
-```{r,include=FALSE}
+```{r}
 #| label: setup
+#| include: false
 # Install required packages
@@
 
-```{r,include=FALSE}
+```{r}
 #| label: read in cleaned and transformed datasets
+#| include: false
 # Read in the cleaned and transformed dataset
@@
 
-```{r,include=FALSE}
+```{r}
 #| label: Source data analysis script
+#| include: false
 source("Source/Data Analysis.R")
@@
 
-```{r, include=FALSE}
+```{r}
 #| label: Prepare for inline character display
+#| include: false
 
@@
 Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old.
-The average age of the sample was `r round(mean(queer.hypo$age), 2)` years old (SD = `r round(sd_age, 2)`).
+The average age of the sample was `r round(mean(queer.hypo$age), 2)` years old (*SD* = `r round(sd_age, 2)`).
 This wide age range ensured the study captured perspectives from individuals across different generations.
-Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (see Fig 1), with both developed and developing country status, providing a global perspective.
+Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective.
 Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender.
 Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender.
-The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (see Fig 2).
+The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2).
 The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native.
@@
 
+```{r}
+#| label: ANOVA tests for psychological well-being scores by different LGBTQ+ subgroups
+#| include: false
+
+# 1. Age
+anova_age_effect <- aov(psychological_wellbeing_score ~ generation, data = queer.hypo)
+summary(anova_age_effect)
+
+# p = .70, no significant difference has been found among different generations
+
+# 2. Residential Country Development Status
+anova_country_effect <- aov(psychological_wellbeing_score ~ development_status, data = queer.hypo)
+summary(anova_country_effect)
+summary_country_effect <- summary(anova_country_effect)[[1]]
+
+# p = .014, F = 6.16, significant difference has been found between developed and developing countries
+
+# 3. Gender identity
+anova_gender_identity_effect <- aov(psychological_wellbeing_score ~ gender_identity_dual, data = queer.hypo)
+summary (anova_gender_identity_effect)
+summary_gender_effect <- summary(anova_gender_identity_effect)[[1]]
+
+# p = .11, no significant difference has been found among different gender identity, but there was a directional effect
+
+# 4. Transgender status
+anova_transgender_effect <- aov(psychological_wellbeing_score ~ transgender, data = queer.hypo)
+summary (anova_transgender_effect)
+
+# p = .25, no significant difference has been found among different gender identity
+
+# 5. Sexual orientation
+anova_sexual_orientation_effect <- aov(psychological_wellbeing_score ~ sexual_orientation, data = queer.hypo)
+summary (anova_sexual_orientation_effect)
+summary_orientation_effect <- summary(anova_sexual_orientation_effect)[[1]]
+
+# p = 0.1, no significant differences have been found among different sexual orientation, but there was directional effect
+
+# 6. Race
+anova_race_effect <- aov(psychological_wellbeing_score ~ race_category, data = queer.hypo)
+summary(anova_race_effect)
+summary_race_effect <- summary(anova_race_effect)[[1]]
+
+# p = .09, marginally significant difference has been found between white and other
+
+```
+
+One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = .70) or between transgenders and non-transgenders (*p* = .25).
+However, significant differences were found between developed and developing countries' residents (Figure 3).
+Specifically, residents in developed countries showed lower psychological impacts scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs.
+$M_{\text{developing}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developing"]), 2)`$; *F*(`r summary_country_effect$Df[1]`, `r summary_country_effect$Df[2]`) = `r round(summary_country_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_country_effect$"Pr(>F)"[1])`).
+
+Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (Figure 4).
+Specifically, men showed lower psychological impacts scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs.
+$M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`).
+The distribution also indicated that men have more low scores than their women or nonbinary counterparts.
+Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations, but there was also a directional effect (Figure 5).
+Specifically, bisexual individuals showed the lowest psychological impacts scores among all sexual orientations, while gay or lesbian had the highest impacts scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).
+
+```{r}
+#| label: fig-plot-country-psych-impact
+#| fig-cap: Country Comparison of Queer Characters' Psychological Impacts
+#| fig-width: 9
+#| fig-height: 5
+
+# Define the theme
+theme.clean <- function(){
+  theme_bw()+
+    theme(axis.text.x = element_text(size = 12, vjust = 1, hjust = 1),
+          axis.text.y = element_text(size = 12),
+          axis.title.x = element_text(size = 14, face = "plain"),             
+          axis.title.y = element_text(size = 14, face = "plain"),
+          panel.grid.major.x = element_blank(),                                          
+          panel.grid.minor.x = element_blank(),
+          panel.grid.minor.y = element_blank(),
+          panel.grid.major.y = element_blank(),  
+          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
+          plot.title = element_text(size = 16, vjust = 1, hjust = 0.5),
+          plot.caption = element_text (size = 8,vjust = 1, hjust = 0.9),
+          legend.text = element_text(size = 12, face = "italic"),          
+          legend.position = "right")}
+
+# Visualization: Boxplot
+
+country_effect_boxplot <- ggplot(queer.hypo, aes(development_status, psychological_wellbeing_score)) + 
+  geom_boxplot(aes(fill = development_status)) +
+  theme_bw() +
+  scale_fill_manual(values = c("#dbf1e5", "#4fba7f")) +               
+  scale_colour_manual(values = c("#dbf1e5", "#4fba7f")) + 
+  labs(title = "Country Comparison of Queer Characters' Psychological Impacts", 
+       x = "Development Status", y = "Queer Characters' Psychological Impact Score") +
+  theme.clean()+
+  theme(axis.text.x = element_text(hjust = 0.5))+
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  stat_summary(fun = mean, geom = "point", color = "black", size = 3, shape = 18, 
+               position = position_dodge(0.75), aes(shape = "Mean"), 
+               show.legend = FALSE) +  
+  stat_summary(fun = mean, geom = "text", aes(label = round(after_stat(y), 2)), 
+               color = "black", vjust = -1, position = position_dodge(0.75), 
+               size = 4, show.legend = FALSE) +
+  labs(fill = "Development Status")
+
+print (country_effect_boxplot)
+
+```
+
+```{r}
+#| label: fig-plot-gender-psych-impact
+#| fig-cap: Gender Identity Difference of Queer Characters' Psychological Impacts
+#| fig-width: 10
+#| fig-height: 5
+
+# Visualization: Violinplot
+
+gender_identity_effect_violinplot <- ggplot(queer.hypo, aes(gender_identity_dual, psychological_wellbeing_score)) + 
+  geom_violin(aes(fill = gender_identity_dual)) +
+  theme_bw() +
+  scale_fill_manual(values = c("#6fa8dc", "#d5a6bd")) +               
+  scale_colour_manual(values = c("#6fa8dc", "#d5a6bd")) + 
+  labs(title = "Gender Identity Difference of Queer Characters' Psychological Impacts", 
+       x = "Gender Identity", y = "Queer Characters' Psychological Impact Score") +
+  theme.clean()+
+  theme(axis.text.x = element_text(hjust = 0.5))+
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  stat_summary(fun = mean, geom = "point", color = "white", size = 3, shape = 18, 
+               position = position_dodge(0.75), aes(shape = "Mean"), 
+               show.legend = FALSE) +  
+  stat_summary(fun = mean, geom = "text", aes(label = round(after_stat(y), 2)), 
+               color = "white", vjust = -1, position = position_dodge(0.75), 
+               size = 4, show.legend = FALSE) +
+  labs(fill = "Gender Identity")
+
+print (gender_identity_effect_violinplot)
+
+```
+
+![Sexual Orientation Comparison of Queer Characters' Psychological Impacts](Image/Fig 10_Orientation_Psych_box.png)
+
+Racial differences in queer media characters’ psychological impacts were marginally significant (Figure 6).
+Specifically, white respondents showed lower psychological impacts scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs.
+$M_{\text{blackother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "Black, Asian, Indian, and Others"]), 2)`$; *F*(`r summary_race_effect$Df[1]`, `r summary_race_effect$Df[2]`) = `r round(summary_race_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_race_effect$"Pr(>F)"[1])`).
+
+```{r}
+#| label: fig-plot-race-psych-impact
+#| fig-cap: Race Comparison of Queer Characters' Psychological Impacts
+#| fig-width: 10
+#| fig-height: 5
+# Visualization: Violinplot
+race_effect_boxplot <- ggplot(queer.hypo, aes(race_category, psychological_wellbeing_score)) + 
+  geom_boxplot(aes(fill = race_category)) +
+  theme_bw() +
+  scale_fill_manual(values = c("#cfb5a0","#f1e2c8")) +               
+  scale_colour_manual(values = c("#cfb5a0","#f1e2c8")) + 
+  labs(title = "Race Comparison of Queer Characters' Psychological Impacts", 
+       x = "Racial Identity", y = "Queer Characters' Psychological Impact Score") +
+  theme.clean()+
+  theme(axis.text.x = element_text(hjust = 0.5))+
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  stat_summary(fun = mean, geom = "point", color = "white", size = 3, shape = 18, 
+               position = position_dodge(0.75), aes(shape = "Mean"), 
+               show.legend = FALSE) +  
+  stat_summary(fun = mean, geom = "text", aes(label = round(after_stat(y), 2)), 
+               color = "white", vjust = -1, position = position_dodge(0.75), 
+               size = 4, show.legend = FALSE) +
+  labs(fill = "Racial Identity")
+
+print (race_effect_boxplot)
+
+```
+
 # Discussion

### 2025-02-11 Manuscript.qmd
Update results for authenticity scores' prediction

@@
 Respondents ranged in age from `r min(queer.hypo$age)` to `r max(queer.hypo$age)` years old.
-The average age of the sample was `r round(mean(queer.hypo$age), 2)` years old (*SD* = `r round(sd_age, 2)`).
+The average age of the sample was `r round(mean(queer.hypo$age), 1)` years old (*SD* = `r round(sd_age, 1)`).
 This wide age range ensured the study captured perspectives from individuals across different generations.
@@
 
+## Predictors of Queer Media Characters’ Psychological Impacts
+
+### Queer Media Consumption Habits
+
+Data visualization of bubble plots revealed that queer media exposure frequency and engagement may predict queer media characters’ psychological impacts on LGBTQ+ individuals.
+The bubble plot for queer media exposure and discussion frequency indicated that developed countries have more participants who engaged less with queer media characters, which may contribute to lower impact scores (Figure 7).
+Though bubbles for developing countries were smaller, it was the result of a much smaller sample size (N = 22) for developing countries' residents than for developed countries' residents (N = 145).
+The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (Figure 8), which may contribute to higher community belong scores and the overall psychological impact scores.
+
+```{r}
+#| label: fig-plot-country-freq
+#| fig-cap: Country Differences in Queer Media Exposure Frequency and Engagement
+#| fig-width: 15
+#| fig-height: 5
+
+create_country_bubble_plot <- function(queer.hypo, y_var, title) {
+  ggplot(queer.hypo, aes(x = development_status, y = !!sym(y_var))) +
+    geom_count(aes(size = ..n..), alpha = 0.6, color = "blue") +  
+    labs(title = title,
+         x = "Development Status",
+         y = y_var) +
+    scale_size_area(max_size = 15, name = "Count") +  
+    theme_minimal() +
+    theme(
+      plot.title = element_text(hjust = 0.5),
+      axis.title.x = element_text(hjust = 0.5),  
+      axis.text.x = element_text(hjust = 0.5),  
+      legend.position = "bottom",  
+      legend.title = element_text(size = 8),
+      legend.text = element_text(size = 7),  
+      legend.key.size = unit(0.5, "cm"),
+      plot.margin = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")  # Reduce margin
+    ) +
+    guides(size = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5))}  # Adjust legend layout
+
+country_freq_bubbleplot <- create_country_bubble_plot(queer.hypo, "frequency", "Frequency")
+country_seek_bubbleplot <- create_country_bubble_plot(queer.hypo, "actively_seek_out", "Actively Seek Out Queer Representations")
+country_discussion_bubbleplot <- create_country_bubble_plot(queer.hypo, "discussion", "Discussion Engagement of Queer Media Representations")
+
+combined_country_bubble_plot <- grid.arrange(country_freq_bubbleplot, country_seek_bubbleplot, country_discussion_bubbleplot, ncol = 3)
+
+```
+
+```{r}
+#| label: fig-plot-gender-freq
+#| fig-cap: Gender Differences in Queer Media Exposure Frequency and Engagement
+#| fig-width: 15
+#| fig-height: 5
+
+create_gender_identity_bubble_plot <- function(queer.hypo, y_var, title) {
+  ggplot(queer.hypo, aes(x = gender_identity_dual, y = !!sym(y_var))) +
+    geom_count(aes(size = ..n..), alpha = 0.6, color = "blue") +  
+    labs(title = title,
+         x = "Gender Identity",
+         y = y_var) +
+    scale_size_area(max_size = 15, name = "Count") +  
+    theme_minimal() +
+    theme(
+      plot.title = element_text(hjust = 0.5),
+      axis.title.x = element_text(hjust = 0.5),  
+      axis.text.x = element_text(hjust = 0.5),  
+      legend.position = "bottom",  
+      legend.title = element_text(size = 8),  
+      legend.text = element_text(size = 7),  
+      legend.key.size = unit(0.5, "cm"),
+      plot.margin = margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")  
+    ) +
+    guides(size = guide_legend(nrow = 1, title.position = "top", title.hjust = 0.5))}
+
+gender_identity_freq_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "frequency", "Frequency")
+gender_identity_seek_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "actively_seek_out", "Actively Seek Out Queer Representations")
+gender_identity_discussion_bubbleplot <- create_gender_identity_bubble_plot(queer.hypo, "discussion", "Discussion Engagement of Queer Media Representations")
+
+combined_gender_identity_bubble_plot <- grid.arrange(gender_identity_freq_bubbleplot, gender_identity_seek_bubbleplot, gender_identity_discussion_bubbleplot, ncol = 3)
+
+```
+
+### Perceived Queer Character Authenticity
+
+```{r}
+#| label: Linear regression for authenticity rating predicting psychological well-being scores
+#| include: false
+
+authenticity.effect <- lm(psychological_wellbeing_score ~ authenticity_rating, data = queer.hypo)
+summary(authenticity.effect)
+
+summary_authenticity <- summary(authenticity.effect)
+
+f_statistic_auth <- summary_authenticity$fstatistic[1]
+df1_auth <- summary_authenticity$fstatistic[2]
+df2_auth <- summary_authenticity$fstatistic[3]
+r_squared_auth <- summary_authenticity$r.squared[1]
+p_value_auth <- pf(f_statistic_auth, df1_auth, df2_auth, lower.tail = FALSE)
+
+```
+
+A linear regression was conducted to examine the relationship between authenticity rating and psychological wellbeing scores.
+The results indicated a significant effect of authenticity rating on psychological wellbeing (*F*(`r df1_auth`, `r df2_auth`) = `r round(f_statistic_auth, 2)`, *p* `r if(p_value_auth < .001) "< .001" else paste("=", round(p_value_auth, 3))`).
+The $R^2$ was `r round(r_squared_auth,3)`, indicating that the perceived queer character authenticity explained `r round(r_squared_auth * 100, 1)`% of the variance in psychological wellbeing scores.
+This result suggests that the more authentic LGBTQ+ individuals perceive queer media characters, the more positive psychological impacts they may experience.
+
+Figure 9 illustrates that the authencity rating positively predicts psychological well-being scores for both developed and developing countries' residents.
+The regression line for developing countries' residents is steeper than that for developed countries' residents, indicating that the authenticity rating has a stronger effect on psychological well-being scores for developing countries' residents.
+
+Figure 10 indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities.
+The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men.
+Nevertheless, given the fact that men have lower psychological impacts scores, the authenticity rating may not be the only factor influencing psychological impact scores.
+
+```{r}
+#| label: fig-plot-auth-psych-impact-country
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Country
+#| message: false
+#| fig-width: 10
+#| fig-height: 5
+auth.psych.dev <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = development_status, shape = development_status)) +                                
+  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Authenticity Rating Predicting Psychological Effects by Development Status") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
+                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = development_status, colour = development_status)) +    
+  scale_colour_manual(name = "Development Status", values = c("#FFC125", "#36648B")) +
+  scale_fill_manual(name = "Development Status",values = c("#FFC125", "#36648B")) +
+  scale_shape_discrete(name = "Development Status") +
+  theme.clean()
+
+print(auth.psych.dev)
+
+```
+
+```{r}
+#| label: fig-plot-auth-psych-impact-gender
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Gender Identity
+#| message: false
+#| fig-width: 10
+#| fig-height: 5.5
+
+auth.psych.gender <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = gender_identity_dual, shape = gender_identity_dual)) +                                
+  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Authenticity Rating Predicting Psychological Effects by Gender Identity") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
+                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = gender_identity_dual, colour = gender_identity_dual)) +    
+  scale_colour_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
+  scale_fill_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
+  scale_shape_discrete(name = "Gender Identity") +
+  theme.clean()
+
+print(auth.psych.gender)
+
+```
+
+Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low scores for both ratings.
+This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of queer media characters.
+
+Figure 12 shows that the authenticity rating positively predicts psychological well-being scores for all racial identities.
+The regression line for black, asian, and indian respondents is slightly steeper, indicating that the authenticity rating has a stronger effect on psychological well-being scores for these respondents.
+This result suggests that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character authenticity than white respondents.
+
+```{r}
+#| label: fig-plot-auth-psych-impact-orientation
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Sexual Orientation
+#| message: false
+#| fig-width: 11
+#| fig-height: 5.5
+
+auth.psych.orientation <- ggplot(queer.hypo_filtered, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = sexual_orientation, shape = sexual_orientation)) +                                
+  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Sexual Orientation") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
+                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = sexual_orientation, colour = sexual_orientation)) +    
+  scale_colour_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
+  scale_fill_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
+  scale_shape_discrete(name = "Sexual Orientation") +
+  facet_wrap(~sexual_orientation) +
+  theme.clean()
+
+print(auth.psych.orientation)
+
+```
+
+```{r}
+#| label: fig-plot-auth-psych-impact-race
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Racial Identity
+#| message: false
+#| fig-width: 11.5
+#| fig-height: 5.5
+
+auth.psych.race <- ggplot(queer.hypo, aes(x = authenticity_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = race_category, shape = race_category)) +                                
+  labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Racial Identity") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$authenticity_rating)), 
+                 ceiling(max(queer.hypo$authenticity_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$authenticity_rating)), ceiling(max(queer.hypo$authenticity_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = race_category, colour = race_category)) +    
+  scale_colour_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
+  scale_fill_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
+  scale_shape_discrete(name = "Racial Identity") +
+  theme.clean()
+
+print(auth.psych.race)
+
+```
+
 # Discussion

### 2025-02-11 Manuscript.qmd
Update results of hypo 2

@@
 
-A linear regression was conducted to examine the relationship between authenticity rating and psychological wellbeing scores.
+A linear regression was conducted to examine the relationship between queer character authenticity rating and psychological wellbeing impact scores.
 The results indicated a significant effect of authenticity rating on psychological wellbeing (*F*(`r df1_auth`, `r df2_auth`) = `r round(f_statistic_auth, 2)`, *p* `r if(p_value_auth < .001) "< .001" else paste("=", round(p_value_auth, 3))`).
@@
 Figure 12 shows that the authenticity rating positively predicts psychological well-being scores for all racial identities.
-The regression line for black, asian, and indian respondents is slightly steeper, indicating that the authenticity rating has a stronger effect on psychological well-being scores for these respondents.
-This result suggests that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character authenticity than white respondents.
+The regression line for black, asian, and indian respondents is slightly steeper, indicating that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character authenticity than white respondents.
 
@@
   labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
-  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Sexual Orientation") + 
+  labs(title = "Authenticity Rating Predicting Psychological Effects by Sexual Orientation") + 
   scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
@@
 #| label: fig-plot-auth-psych-impact-race
-#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Racial Identity
+#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Racial Identity
 #| message: false
@@
   labs(x = "Authenticity Rating", y = "Queer Characters' Psychological Impact Score") +
-  labs(title = "Authenticity Rating's Impacts on Queer Characters' Psychological Effects by Racial Identity") + 
+  labs(title = "Authenticity Rating Predicting Psychological Effects by Racial Identity") + 
   scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
@@
   stat_smooth(method = "lm", aes(fill = race_category, colour = race_category)) +    
-  scale_colour_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
-  scale_fill_manual(name = "Racial Identity", values = c("#cfb5a0","#f1e2c8")) +
+  scale_colour_manual(name = "Racial Identity", values = c("black", "#cfb5a0")) +
+  scale_fill_manual(name = "Racial Identity", values = c("black","#cfb5a0")) +
   scale_shape_discrete(name = "Racial Identity") +
@@
 print(auth.psych.race)
+
+```
+
+### Perceived Queer Character Intersectionality
+
+```{r}
+#| label: Linear regression for intersectionality rating predicting psychological well-being scores
+#| include: false
+
+inter.effect <- lm(psychological_wellbeing_score ~ intersectionality_rating, data = queer.hypo)
+summary(inter.effect)
+
+summary_intersectionality <- summary(inter.effect)
+
+f_statistic_inter <- summary_intersectionality$fstatistic[1]
+df1_inter <- summary_intersectionality$fstatistic[2]
+df2_inter <- summary_intersectionality$fstatistic[3]
+r_squared_inter <- summary_intersectionality$r.squared[1]
+p_value_inter <- pf(f_statistic_inter, df1_inter, df2_inter, lower.tail = FALSE)
+
+```
+
+Linear regression results also indicated a significant effect of queer character intersectionality rating on psychological wellbeing impact scores (*F*(`r df1_inter`, `r df2_inter`) = `r round(f_statistic_inter, 2)`, *p* `r if(p_value_inter < .001) "< .001" else paste("=", round(p_value_inter, 3))`).
+The $R^2$ was `r round(r_squared_inter,3)`, indicating that the perceived queer character authenticity explained `r round(r_squared_inter * 100, 1)`% of the variance in psychological wellbeing scores.
+This robust association suggests that LGBTQ+ individuals who perceive queer media characters as more intersectional tend to experience more positive psychological outcomes.
+
+Figure 13 further indicated that queer characters' intersectionality may be a more significant contributor to psychological impact scores for developing countries' residents than for developed countries' residents.
+The regression line for developing countries' residents is steeper, with no intersectionality ratings lower than the middle point.
+Conversely, the regression line for developed countries' residents is flatter, with more low intersectionality ratings and psychological impact scores.
+
+Though the regressioin line slopes for different gender identities were similar regarding intersectionality rating's effects on psychological impact scores, data points for women and other gender identities were more concentrated on the higher end, with lower intersectionality scores predicting relatively higher psychological impact scores than their men counterparts (Figure 14).
+Men respondents featured more low psychological impact data points even when the intersectionality rating was high.
+This indicates that the intersectionality rating may contribute to higher psychological impact scores for women and other gender identities, which could be a plausible explanation of men's lower psychological impact scores even if the authenticity ratings predict higher scores for men compared with women and other gender identities.
+
+```{r}
+#| label: fig-plot-inter-psych-impact-country
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Country
+#| message: false
+#| fig-width: 10
+#| fig-height: 5
+
+inter.psych.dev <- ggplot(queer.hypo, aes(x = intersectionality_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = development_status, shape = development_status)) +                                
+  labs(x = "Intersectionality Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Intersectionality Rating Predicting Psychological Effects by Development Status") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$intersectionality_rating)), 
+                 ceiling(max(queer.hypo$intersectionality_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$intersectionality_rating)), ceiling(max(queer.hypo$intersectionality_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = development_status, colour = development_status)) +    
+  scale_colour_manual(name = "Development Status", values = c("#FFC125", "#36648B")) +
+  scale_fill_manual(name = "Development Status",values = c("#FFC125", "#36648B")) +
+  scale_shape_discrete(name = "Development Status") +
+  theme.clean()
+
+print(inter.psych.dev)
+
+```
+
+```{r}
+#| label: fig-plot-inter-psych-impact-gender
+#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Gender Identity
+#| message: false
+#| fig-width: 10
+#| fig-height: 5.5
+
+inter.psych.gender <- ggplot(queer.hypo, aes(x = intersectionality_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = gender_identity_dual, shape = gender_identity_dual)) +                                
+  labs(x = "Intersectionality Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Intersectionality Rating Predicting Psychological Effects by Gender Identity") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$intersectionality_rating)), 
+                 ceiling(max(queer.hypo$intersectionality_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$intersectionality_rating)), ceiling(max(queer.hypo$intersectionality_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = gender_identity_dual, colour = gender_identity_dual)) +    
+  scale_colour_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
+  scale_fill_manual(name = "Gender Identity", values = c("#6fa8dc", "#d5a6bd")) +
+  scale_shape_discrete(name = "Gender Identity") +
+  theme.clean()
+
+print(inter.psych.gender)
+
+```
+
+Based on the finding that intersectionality rating contributed to higher psychological impact scores for women and other gender identities, Figure 15 compared both gender identity and sexual orientation on differences in intersectionality rating's prediction of psychological impact scores.
+The results indicated that intersectionality rating was a stronger predictor of psychological impact scores for bisexual men compared with bisexual women and other gender identities, with a steeper regression line.
+Nevertheless, the regression line for lesbian women is slightly steeper than gay men, indicating that intersectionality rating may have a stronger effect on psychological impact scores for lesbian than gay.
+It is worth noting that while the associations between intersectionality rating and psychological impact scores were positive among asexual and pansexual women with relatively small variations, the associations were negative among asexual and pansexual men with more variations and data point proportion below the regression line.
+Thus, it is plausiable that the negative associations contributed significantly to the lower psychological impact scores predicted by the intersectionality rating for men respondents.
+
+```{r}
+#| label: fig-plot-inter-psych-impact-orientation-gender
+#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Sexual Orientation and Gender Identity
+#| message: false
+#| warning: false
+#| fig-width: 12
+#| fig-height: 5.5
+
+inter.psych.orientation.gender <- ggplot(queer.hypo_filtered, aes(x = intersectionality_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = sexual_orientation, shape = sexual_orientation)) +                                
+  labs(x = "Intersectionality Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Intersectionality Rating Predicting Psychological Effects by Sexual Orientation and Gender Identity") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$intersectionality_rating)), 
+                 ceiling(max(queer.hypo$intersectionality_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$intersectionality_rating)), ceiling(max(queer.hypo$intersectionality_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = sexual_orientation, colour = sexual_orientation)) +    
+  scale_colour_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
+  scale_fill_manual(name = "Sexual Orientation", values = c("#A3A3A3","#9B4F96","#3D1A78","#FFD800")) +
+  scale_shape_discrete(name = "Sexual Orientation") +
+  facet_grid(gender_identity_dual ~ sexual_orientation) +
+  theme.clean() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        strip.text = element_text(size = 8),
+        legend.position = "bottom")
+
+print(inter.psych.orientation.gender)
+
+```
+
+Figure 16 illustrates that the intersectionality rating positively predicts psychological well-being scores for all racial identities.
+The regression line for black, asian, and indian respondents is steeper with more data points concentrated on the higher end of the intersectionality rating and psychological impact scores.
+This indicates that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character intersectionality than white respondents.
+
+```{r}
+#| label: fig-plot-inter-psych-impact-race
+#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Racial Identity
+#| message: false
+#| fig-width: 11.5
+#| fig-height: 5.5
+
+inter.psych.race <- ggplot(queer.hypo, aes(x = intersectionality_rating, y = psychological_wellbeing_score)) +
+  geom_point(aes(colour = race_category, shape = race_category)) +                                
+  labs(x = "Intersectionality Rating", y = "Queer Characters' Psychological Impact Score") +
+  labs(title = "Intersectionality Rating Predicting Psychological Effects by Racial Identity") + 
+  scale_y_continuous(breaks = seq(floor(min(queer.hypo$psychological_wellbeing_score)), 
+                                  ceiling(max(queer.hypo$psychological_wellbeing_score)), by = 1)) +
+  scale_x_continuous(
+    breaks = seq(floor(min(queer.hypo$intersectionality_rating)), 
+                 ceiling(max(queer.hypo$intersectionality_rating)), by = 1),
+    limits = c(floor(min(queer.hypo$intersectionality_rating)), ceiling(max(queer.hypo$intersectionality_rating)))
+  ) +
+  stat_smooth(method = "lm", aes(fill = race_category, colour = race_category)) +    
+  scale_colour_manual(name = "Racial Identity", values = c("black", "#cfb5a0")) +
+  scale_fill_manual(name = "Racial Identity", values = c("black", "#cfb5a0")) +
+  scale_shape_discrete(name = "Racial Identity") +
+  theme.clean()
+
+print(inter.psych.race)
 

### 2025-02-11 Source/Data Analysis.R
Update comments

@@ -1006,7 +1006,6 @@ inter.psych.orientation.gender <- ggplot(queer.hypo_filtered, aes(x = intersecti
 
 print(inter.psych.orientation.gender)
 
-# Bisexual men are more likely to have extreme values for intersectionality rating and psychological impact scores on the lower side, bisexual women feature higher intersectionality and psychological impact scores
 # Gay have more variances
 # Asexual and pansexual women are more likely to draw the positive relationship between intersectionality and psychological impacts, while asexual and pansexual men are more likely to have the negative relationship
 

### 2025-02-13 Manuscript.qmd
Update discussion and conclusion

@@
 The bubble plot for queer media exposure and discussion frequency indicated that developed countries have more participants who engaged less with queer media characters, which may contribute to lower impact scores (Figure 7).
-Though bubbles for developing countries were smaller, it was the result of a much smaller sample size (N = 22) for developing countries' residents than for developed countries' residents (N = 145).
-The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (Figure 8), which may contribute to higher community belong scores and the overall psychological impact scores.
+Though bubbles for developing countries were smaller, it was the result of a much smaller sample size (*n* = 22) for developing countries' residents than for developed countries' residents (*n* = 145).
+The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (Figure 8), which may contribute to higher community belonging scores and the overall psychological impact scores.
 
@@
 
-## Limitations and Future Directions
+## Queer Media Characters' Psychological Impacts on Different LGBTQ+ Subgroups
+
+The results of the study indicated that queer media characters' psychological impacts on LGBTQ+ individuals did not significantly differ among different generations.
+This finding suggests that queer media representations may have become more diverse in age over time, catering to different generations of LGBTQ+ individuals.
+It is also consistent with @dhoest_queer_2022, which found that LGBTQ+ individuals across all generations were keen to watch LGBTQ-themed films and rated TV shows featuring LGBTQ+ characters as important.
+The recent years' increase in transgender media representation may have contributed to the positive psychological impacts on transgender individuals, resulting in the insignificant differences between transgender and non-transgender individuals.
+For instance, the number of transgender characters on broadcast TV increased from two characters in 2014 to 24 characters in 2024 [@GLAAD2024].
+Reality shows such as *RuPaul's Drag Race* and TV series like *Pose* and *Euphoria* were also popular among transgender participants in this study.
+
+The study has also found that queer media characters' psychological impacts on LGBTQ+ individuals were less significant for individuals living in developed countries than for those living in developing countries.
+A plausible explanation could be a higher saturation of queer characters in media leading to a normalization of queer identities in developed countries.
+As a result, the impact of individual characters may be less pronounced, as audiences become desensitized to their presence.
+In contrast, the scarcity of queer characters in developing countries may lead to a more profound impact when they appear.
+Additionally, LGBTQ+ individuals in developed countries might have more access to mental health resources and support systems (e.g., LGBTQ+ advocacy groups), which could mitigate the effects of media representations on psychological well-being.
+Nevertheless, LGBTQ+ individuals in developing countries may rely more on cultural resources such as queer media characters for representation and community belonging, leading to a stronger psychological impact.
+
+Regarding gender identity and racial identity, the study found that queer media characters' psychological impacts on LGBTQ+ individuals were more positive for gender and racial minorities.
+These findings reflected that queer media representations have become more diverse in gender and racial identities.
+Specifically, @GLAAD2024 reported 2024 as the fifth year there were more LGBTQ+ women than men on broadcast, with 58% were women or nonbinary, and 42% were men.
+Regarding racial identity, the number of LGBTQ+ characters of color on broadcast TV increased from 23% in 2014 to 50% in 2024, with 30% of LGBTQ+ characters being Black, 7% Latine, 5% Asian, and 8% multiracial or others.
+This shift in decades of LGBTQ+ representation may have contributed to the more positive psychological impacts on gender and racial minorities.
+
+Nevertheless, the study found that regarding sexual orientation, the mainstream group (i.e., gay or lesbian) had the highest psychological impact scores, while bisexual respondents had the lowest.
+This is consistent with @GLAAD2024's report that the percentage of bisexual characters on broadcast TV was significantly lower than the percentage of bisexual as the majority in the LGBTQ+ community (24% vs.
+58%).
+Apart from this disparity, the bi+ erasure (i.e., the tendency to not specify a character as bisexual) in media may have also contributed to the lower psychological impact scores on bisexual respondents.
+The following section further discusses the potential explanations from the perspectives of perceived character authenticity and intersectionality.
+
+## Predictors of Queer Media Characters’ Psychological Impacts
+
+This study found that the frequency of queer media exposure and discussion engagement may predict psychological impacts.
+Specifically, the results indicated that more respondents in developed countries had lower exposure to queer media characters (e.g., a few times per year), which may contribute to lower psychological impact scores.
+This finding suggests that the normalization of queer characters and more well-established social support systems for LGBTQ+ individuals in developed countries may have led to a desensitization effect, reducing the psychological impacts of queer characters.
+Regarding queer media discussion engagement, the results revealed that women and nonbinary individuals had higher discussion engagement than men, which may contribute to higher community belonging scores and overall psychological impact scores.
+This finding also highlights that there may not be enough online forums or platforms specifically tailored to the needs and interests of queer men.
+Additionally, social norms and expectations around masculinity may discourage queer men from openly discussing their experiences or engaging in vulnerable conversations that reveal their identities.
+These norms often penalize emotional expressiveness in men, which might make them less likely to participate in discussions that require self-disclosure, resulting in lower community belonging scores.
+
+The study also revealed that perceived queer character authenticity and intersectionality are strongly positively related to queer characters' psychological impact scores.
+The more authentic and intersectional LGBTQ+ individuals perceive queer media characters, the more positive psychological impacts they may experience.
+This is consistent with previous research that the amplification of stereotypes and lack of intersectional representation in media can lead to negative psychological outcomes for marginalized groups [@nolke_making_2018].
+The findings suggest that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals given the high explanatory power.
+
+The correlations between authenticity and intersectionality ratings and psychological impact scores also explain the disparities in psychological impacts among different LGBTQ+ subgroups, especially for sexuality.
+Regarding gender identity, authenticity rating has a stronger effect on psychological impact scores for men than women and other gender identity.
+This finding suggests that queer men may be more sensitive to whether media representations feel authentic or genuine.
+This sensitivity could stem from past experiences with harmful stereotypes or depictions such as ‘perfect homo’ of queer men in media.
+The lower psychological impact scores for queer men could also result from more existing queer men stereotypes in the media than women and other gender identities.
+Additionally, queer men respondents were less sensitive to intersectionality rating since there was a significant proportion of the data points featuring high intersectionality with low psychological impact scores.
+This suggests that queer men might prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities.
+Meanwhile, queer men who face fewer intersectional challenges may not feel represented by narratives that emphasize multiple forms of marginalization, leading to lower psychological benefit from such representations.
+Thus, the recent progress in queer media characters' intersectionality may result in more positive psychological impacts on women and other gender identities, as they were more invisible and marginalized before.
+This also applies to racial identity, where the intersectionality rating has a stronger effect on psychological impact scores for black, asian, and indian respondents than white respondents as they may have experienced more intersectional challenges in their lives.
+The higher psychological impact scores for racial minorities may also result from the recent increase in racial minority representation in queer media characters that feature more intersectional identities.
+
+It is worth noting that authenticity and intersectionality ratings may also play a significant role in explaining the disparities in psychological impacts among different sexual orientations.
+Among all sexual orientations, only bisexual respondents had more data points condensed on the lower end of the authenticity rating and psychological impact scores.
+This suggests that bisexual respondents' low psychological impacts scores may be related to the perceived low authenticity of bisexual media characters.
+While bisexual men are often depicted as secretly gay with absence of bisexual representations, biseuxal women are often depicted as hypersexualized or fetishized [@young_why_2022].
+This can further reinforce the stigma and stereotypes surrounding bisexuality as creedy or indecisive, perpetuating biphobia in society.
+The negative associations between intersectionality rating and psychological impact scores for asexual and pansexual men further indicated that queer men may prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities as there was barely any asexual or pansexual men in the media.
 
 ## Conclusion
+This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts.
+The findings indicate that while queer media characters' psychological impacts do not significantly differ among different generations and transgender status, they are more positive for individuals living in developing countries, women and nonbinary individuals, gay or lesbian, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years.
+The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals.
+While queer men may be more sensitive to authenticity due to existing stereotypes, queer women and other identities tend to benefit more from intersectional representations.
+Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in media.
+The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diversified queer images.
+It is also necessary to present bisexual characters in a non-stereotypical way to reduce biphobia and increase bisexual individuals' psychological well-being.
+The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups by sample size, and lack of comparison among different media’s impacts.
+Future research may consider a larger sample with more balanced representation of different subgroups to further explore the psychological impacts of queer media characters on LGBTQ+ individuals.
+Scholars may also be interested in the intersectional analysis of different media’s impacts.
 
@@
 :::
-
-# Appendix
-
-# Title for Appendix

### 2025-02-13 Manuscript.qmd
Update manuscript

@@
 While previous studies have explored the double-edged impact of queer media representation on LGBTQ+ individuals’ development, few have compared these effects across different LGBTQ+ subgroups.
-This study investigates queer media characters’ psychological impacts on LGBTQ+ individuals with different identities, examining the relationship between perceived character authenticity, intersectionality, and characters’ impacts on LGBTQ+ individuals’ psychological well-being using a reliable survey instrument in a worldwide sample.
+This study investigates queer media characters’ psychological impacts on LGBTQ+ individuals with different identities, examining the relationship between queer media consumption, perceived character authenticity, intersectionality, and queer characters' psychological impact scores using a reliable survey instrument in a worldwide sample.
 
@@
 However, in terms of sexual orientation, mainstream groups (i.e., gay and lesbian respondents) showed higher scores.
-Importantly, the study found strong positive correlations between authenticity ratings, intersectionality ratings, and scores of queer characters’ positive impacts on psychological well-being.
+Importantly, the study found strong positive correlations between authenticity ratings, intersectionality ratings, and scores of queer characters’ positive impacts on LGBTQ+ individuals' psychological well-being.
 
@@
 The first research question investigated whether there were differences in queer characters’ psychological impacts among LGBTQ+ individuals with different identities.
-Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, races, ages, and residential countries on queer characters’ psychological impacts.
-Given the fact that there were still queer stereotypes and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents).
+Specifically, this study has compared LGBTQ+ individuals with different sexual orientations, gender identities, racial identities, ages, and residential countries on queer characters’ psychological impacts.
+Given the fact that there were still absences of marginalized identities and fewer intersectional representations in mass media, the current study stated that queer media characters’ positive impacts on psychological well-being would be weaker for LGBTQ+ individuals with more invisible and marginalized identities (e.g., asexual, transgender, black, elder generations, developing countries’ residents) while being stronger for those with more visible identities (e.g., gay, cisgender, white, younger generations, developed countries’ residents).
 The second research question asked whether queer media consumption patterns, perceived character authenticity, and perceived character intersectionality can predict queer media characters’ psychological impacts.
-Specifically, this study hypothesized that lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impacts.
-Conversely, higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impacts.
+Specifically, this study hypothesized that lower exposure to queer media representations, and lower ratings for perceived character authenticity and intersectionality would result in lower ratings for queer characters’ positive psychological impact scores.
+Conversely, higher engagement with queer media representations, and higher ratings for perceived character authenticity and intersectionality would result in higher ratings for queer characters’ positive psychological impact scores.
 
@@
 ### Reliability Tests
-Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (see Table 1).
+Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (Table 1).
 Cronbach's alpha coefficients were calculated for each scale.
@@
 Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective.
-Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as non-binary, genderfluid, gender non-conforming, or agender.
+Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as nonbinary, genderfluid, gender non-conforming, or agender.
 Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender.
@@
 The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native.
-This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersecting identities.
+This rich diversity in age (generation), residential country, gender identity, sexual orientation, and racial identity enables meaningful comparisons and analyses across various LGBTQ+ subgroups and their intersectional identities.
 
@@
 
-One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = .70) or between transgenders and non-transgenders (*p* = .25).
+One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = 0.70) or between transgenders and non-transgenders (*p* = 0.25).
 However, significant differences were found between developed and developing countries' residents (Figure 3).
-Specifically, residents in developed countries showed lower psychological impacts scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs.
+Specifically, residents in developed countries showed lower psychological impact scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs.
 $M_{\text{developing}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developing"]), 2)`$; *F*(`r summary_country_effect$Df[1]`, `r summary_country_effect$Df[2]`) = `r round(summary_country_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_country_effect$"Pr(>F)"[1])`).
@@
 Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (Figure 4).
-Specifically, men showed lower psychological impacts scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs.
+Specifically, men showed lower psychological impact scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs.
 $M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`).
-The distribution also indicated that men have more low scores than their women or nonbinary counterparts.
-Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations, but there was also a directional effect (Figure 5).
-Specifically, bisexual individuals showed the lowest psychological impacts scores among all sexual orientations, while gay or lesbian had the highest impacts scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).
+The distribution also indicated that men have more low score distributions than their women or nonbinary counterparts.
+Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations.
+Nevertheless, there was also a directional effect (Figure 5).
+Specifically, bisexual individuals showed the lowest psychological impact scores among all sexual orientations, while gay or lesbian had the highest impact scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).
 
@@
 Racial differences in queer media characters’ psychological impacts were marginally significant (Figure 6).
-Specifically, white respondents showed lower psychological impacts scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs.
+Specifically, white respondents showed lower psychological impact scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs.
 $M_{\text{blackother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "Black, Asian, Indian, and Others"]), 2)`$; *F*(`r summary_race_effect$Df[1]`, `r summary_race_effect$Df[2]`) = `r round(summary_race_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_race_effect$"Pr(>F)"[1])`).
@@
 #| label: fig-plot-race-psych-impact
-#| fig-cap: Race Comparison of Queer Characters' Psychological Impacts
+#| fig-cap: Racial Comparison of Queer Characters' Psychological Impacts
 #| fig-width: 10
@@
   scale_colour_manual(values = c("#cfb5a0","#f1e2c8")) + 
-  labs(title = "Race Comparison of Queer Characters' Psychological Impacts", 
+  labs(title = "Racial Comparison of Queer Characters' Psychological Impacts", 
        x = "Racial Identity", y = "Queer Characters' Psychological Impact Score") +
@@
 The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men.
-Nevertheless, given the fact that men have lower psychological impacts scores, the authenticity rating may not be the only factor influencing psychological impact scores.
+Nevertheless, given the fact that men have lower psychological impact scores, the authenticity rating may not be the only factor influencing psychological impact scores.
 
@@
 
-Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low scores for both ratings.
-This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of queer media characters.
+Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.
+It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low score distributions for both ratings.
+This result suggests that bisexual respondents' low psychological impacts scores may be related to the perceived authenticity of bisexual media characters.
 
@@
 #| label: fig-plot-auth-psych-impact-race
-#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Racial Identity
+#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Racial Identity
 #| message: false
@@
 Linear regression results also indicated a significant effect of queer character intersectionality rating on psychological wellbeing impact scores (*F*(`r df1_inter`, `r df2_inter`) = `r round(f_statistic_inter, 2)`, *p* `r if(p_value_inter < .001) "< .001" else paste("=", round(p_value_inter, 3))`).
-The $R^2$ was `r round(r_squared_inter,3)`, indicating that the perceived queer character authenticity explained `r round(r_squared_inter * 100, 1)`% of the variance in psychological wellbeing scores.
-This robust association suggests that LGBTQ+ individuals who perceive queer media characters as more intersectional tend to experience more positive psychological outcomes.
+The $R^2$ was `r round(r_squared_inter,3)`, indicating that the perceived queer character intersectionality explained `r round(r_squared_inter * 100, 1)`% of the variance in psychological wellbeing scores.
+This robust association suggests that LGBTQ+ individuals who perceive queer media characters as more intersectional and diverse tend to experience more positive psychological outcomes.
 
@@
 #| label: fig-plot-inter-psych-impact-country
-#| fig-cap: Authenticity Rating Predicting Psychological Well-being Scores by Country
+#| fig-cap: Intersectionality Rating Predicting Psychological Well-being Scores by Country
 #| message: false
@@
 This finding suggests that queer media representations may have become more diverse in age over time, catering to different generations of LGBTQ+ individuals.
-It is also consistent with @dhoest_queer_2022, which found that LGBTQ+ individuals across all generations were keen to watch LGBTQ-themed films and rated TV shows featuring LGBTQ+ characters as important.
-The recent years' increase in transgender media representation may have contributed to the positive psychological impacts on transgender individuals, resulting in the insignificant differences between transgender and non-transgender individuals.
+It is also consistent with findings from @dhoest_queer_2022, which found that LGBTQ+ individuals across all generations were keen to watch LGBTQ-themed films and rated TV shows featuring LGBTQ+ characters as important.
+The recent years' increase in transgender media representation may have contributed to the positive psychological impacts on transgender respondents, resulting in the insignificant differences between transgender and non-transgender individuals.
 For instance, the number of transgender characters on broadcast TV increased from two characters in 2014 to 24 characters in 2024 [@GLAAD2024].
@@
 A plausible explanation could be a higher saturation of queer characters in media leading to a normalization of queer identities in developed countries.
-As a result, the impact of individual characters may be less pronounced, as audiences become desensitized to their presence.
+As a result, the impact of individual characters may be less pronounced since audiences become desensitized to their presence.
 In contrast, the scarcity of queer characters in developing countries may lead to a more profound impact when they appear.
@@
 Regarding gender identity and racial identity, the study found that queer media characters' psychological impacts on LGBTQ+ individuals were more positive for gender and racial minorities.
-These findings reflected that queer media representations have become more diverse in gender and racial identities.
-Specifically, @GLAAD2024 reported 2024 as the fifth year there were more LGBTQ+ women than men on broadcast, with 58% were women or nonbinary, and 42% were men.
-Regarding racial identity, the number of LGBTQ+ characters of color on broadcast TV increased from 23% in 2014 to 50% in 2024, with 30% of LGBTQ+ characters being Black, 7% Latine, 5% Asian, and 8% multiracial or others.
+These findings reflect that queer media representations have become more diverse in gender and racial identities.
+Specifically, @GLAAD2024 reported 2024 as the fifth year there were more queer women than men on broadcast, with 58% women or nonbinary, and 42% men characters.
+Regarding racial identity, the number of LGBTQ+ characters of color on broadcast TV increased from 23% in 2014 to 50% in 2024, with 30% of LGBTQ+ characters being black, 7% Latine, 5% asian, and 8% multiracial or others.
 This shift in decades of LGBTQ+ representation may have contributed to the more positive psychological impacts on gender and racial minorities.
@@
 58%).
-Apart from this disparity, the bi+ erasure (i.e., the tendency to not specify a character as bisexual) in media may have also contributed to the lower psychological impact scores on bisexual respondents.
+Apart from this disparity, the bi+ erasure (i.e., the tendency to not specify a character as bisexual) in media may have also contributed to the lower psychological impact scores of bisexual respondents.
 The following section further discusses the potential explanations from the perspectives of perceived character authenticity and intersectionality.
@@
 This finding also highlights that there may not be enough online forums or platforms specifically tailored to the needs and interests of queer men.
-Additionally, social norms and expectations around masculinity may discourage queer men from openly discussing their experiences or engaging in vulnerable conversations that reveal their identities.
-These norms often penalize emotional expressiveness in men, which might make them less likely to participate in discussions that require self-disclosure, resulting in lower community belonging scores.
+Additionally, social norms and expectations around masculinity may discourage queer men from openly discussing their experiences or engaging in vulnerable conversations that reveal their identities, resulting in lower community belonging scores.
 
@@
 This is consistent with previous research that the amplification of stereotypes and lack of intersectional representation in media can lead to negative psychological outcomes for marginalized groups [@nolke_making_2018].
-The findings suggest that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals given the high explanatory power.
 
@@
 Regarding gender identity, authenticity rating has a stronger effect on psychological impact scores for men than women and other gender identity.
-This finding suggests that queer men may be more sensitive to whether media representations feel authentic or genuine.
-This sensitivity could stem from past experiences with harmful stereotypes or depictions such as ‘perfect homo’ of queer men in media.
+This finding suggests that queer men may be more sensitive to whether queer media representations feel authentic or genuine.
+This sensitivity could stem from past experiences with harmful stereotypes or depictions such as ‘perfect homo’ of queer men in the media.
 The lower psychological impact scores for queer men could also result from more existing queer men stereotypes in the media than women and other gender identities.
@@
 This suggests that queer men might prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities.
-Meanwhile, queer men who face fewer intersectional challenges may not feel represented by narratives that emphasize multiple forms of marginalization, leading to lower psychological benefit from such representations.
 Thus, the recent progress in queer media characters' intersectionality may result in more positive psychological impacts on women and other gender identities, as they were more invisible and marginalized before.
@@
 
-It is worth noting that authenticity and intersectionality ratings may also play a significant role in explaining the disparities in psychological impacts among different sexual orientations.
+It is worth noting that authenticity and intersectionality ratings may also play a significant role in explaining the disparities in psychological impact among different sexual orientations.
 Among all sexual orientations, only bisexual respondents had more data points condensed on the lower end of the authenticity rating and psychological impact scores.
@@
 While bisexual men are often depicted as secretly gay with absence of bisexual representations, biseuxal women are often depicted as hypersexualized or fetishized [@young_why_2022].
-This can further reinforce the stigma and stereotypes surrounding bisexuality as creedy or indecisive, perpetuating biphobia in society.
+This can further reinforce the stigma and stereotypes surrounding bisexuality as greedy or indecisive, perpetuating biphobia in society.
 The negative associations between intersectionality rating and psychological impact scores for asexual and pansexual men further indicated that queer men may prioritize or respond more strongly to characters that focus primarily on their sexual orientation rather than on intersectional identities as there was barely any asexual or pansexual men in the media.
@@
 This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts.
-The findings indicate that while queer media characters' psychological impacts do not significantly differ among different generations and transgender status, they are more positive for individuals living in developing countries, women and nonbinary individuals, gay or lesbian, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years.
+The findings indicate that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years.
 The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals.
 While queer men may be more sensitive to authenticity due to existing stereotypes, queer women and other identities tend to benefit more from intersectional representations.
-Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in media.
-The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diversified queer images.
+Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in the media.
+The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diverse queer representations.
 It is also necessary to present bisexual characters in a non-stereotypical way to reduce biphobia and increase bisexual individuals' psychological well-being.
-The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups by sample size, and lack of comparison among different media’s impacts.
+The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups, and the lack of comparison among different media’s impacts.
 Future research may consider a larger sample with more balanced representation of different subgroups to further explore the psychological impacts of queer media characters on LGBTQ+ individuals.

### 2025-02-13 Queer Characters and LGBTQ+ Well-being.qmd
Dingning Yang - Project submission #1 for grading - @nrdowling @Regenchen

--- 2025-02-13 Manuscript.qmd
@@
 This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts.
-The findings indicate that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years.
+The findings indicated that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years.
 The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals.

### 2025-02-18 Queer Characters and LGBTQ+ Well-being.qmd
Update table and figure references (objective 24)

@@
 bibliography: References.bib
+
 ---
@@
 ### Reliability Tests
-Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (Table 1).
+Reliability analyses were conducted to assess the internal consistency of the measurement scales used in this study (@tbl-reliability).
 Cronbach's alpha coefficients were calculated for each scale.
@@
 ```{r}
-#| label: Generate reliability test tables
+#| label: tbl-reliability
+#| tbl-cap: "Reliability Analysis Results"
 #| echo: false
@@
 #| message: false
-#| tbl-cap: "Reliability Analysis Results"
 
@@
 kable(reliability_kable, 
-      caption = "Reliability Tests Results",
       col.names = c("Scale", "Number of Items", "Cronbach's alpha", "Interpretation"),
       align = c("l", "c", "c", "c"),
-      booktabs = TRUE,
-      format = "latex") %>%
+      booktabs = TRUE) %>%
   kable_styling(latex_options = c("striped", "hold_position"),
-                full_width = FALSE) %>%
+                full_width = FALSE,
+                ) %>% 
   column_spec(1, width = "5cm") %>%
@@
 This wide age range ensured the study captured perspectives from individuals across different generations.
-Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (Figure 1), with both developed and developing country status, providing a global perspective.
+Respondents' residential countries included `r n_distinct (queer.hypo.country$country)` countries and four continents (@fig-residential), with both developed and developing country status, providing a global perspective.
 Regarding sexuality, the sample featured a diverse range of identities, with `r round(100 * sum(queer.hypo$gender_identity == "Man") / nrow(queer.hypo), 1)`% identifying as men, `r round(100 * sum(queer.hypo$gender_identity == "Woman") / nrow(queer.hypo), 1)`% as women, and 10.2% as nonbinary, genderfluid, gender non-conforming, or agender.
 Among the sample, `r round(100 * sum(queer.hypo$transgender == "Yes") / nrow(queer.hypo), 1)`% was identified as transgender.
-The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (Figure 2).
+The sexual orientation distribution of participants was also diverse, featuring `r sexual_orientation_inline` (@fig-sexuality).
 The racial distribution of the sample covered `r round(100 * sum(queer.hypo$race == "White") / nrow(queer.hypo), 1)`% white respondents, `r round(100 * sum(queer.hypo$race == "Black or African-American") / nrow(queer.hypo), 1)`% black or African-American respondents, and 15.5% Asian, Indian, or Alaska native.
@@
 
-![Sexuality Distribution](Image/Fig 03_Gender identity_Transgender status_Sexual orientation_pie.png)
+![Sexuality Distribution](Image/Fig 03_Gender identity_Transgender status_Sexual orientation_pie.png){#fig-sexuality}
 
@@
 One-way ANOVA results showed that there were no significant differences or directional effects in queer media characters’ psychological impacts among different generations (*p* = 0.70) or between transgenders and non-transgenders (*p* = 0.25).
-However, significant differences were found between developed and developing countries' residents (Figure 3).
+However, significant differences were found between developed and developing countries' residents (@fig-plot-country-psych-impact).
 Specifically, residents in developed countries showed lower psychological impact scores by queer media characters than those in developing countries ($M_{\text{developed}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developed"]), 2)`$ vs.
 $M_{\text{developing}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$development_status == "Developing"]), 2)`$; *F*(`r summary_country_effect$Df[1]`, `r summary_country_effect$Df[2]`) = `r round(summary_country_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_country_effect$"Pr(>F)"[1])`).
-
-Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (Figure 4).
-Specifically, men showed lower psychological impact scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs.
-$M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`).
-The distribution also indicated that men have more low score distributions than their women or nonbinary counterparts.
-Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations.
-Nevertheless, there was also a directional effect (Figure 5).
-Specifically, bisexual individuals showed the lowest psychological impact scores among all sexual orientations, while gay or lesbian had the highest impact scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).
 
@@
 
+Though the ANOVA result did not show significant differences among different gender identities, there was a directional effect indicated by the violin plot (@fig-plot-gender-psych-impact).
+Specifically, men showed lower psychological impact scores than women and other gender identities ($M_{\text{men}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Man"]), 2)`$ vs.
+$M_{\text{womenother}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$gender_identity_dual == "Women, or nonbinary, or agender"]), 2)`$; *F*(`r summary_gender_effect$Df[1]`, `r summary_gender_effect$Df[2]`) = `r round(summary_gender_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_gender_effect$"Pr(>F)"[1])`).
+The distribution also indicated that men have more low score distributions than their women or nonbinary counterparts.
+Regarding sexual orientation, the ANOVA result did not show significant differences among different sexual orientations.
+Nevertheless, there was also a directional effect (@fig-plot-orientation-psych-impact).
+Specifically, bisexual individuals showed the lowest psychological impact scores among all sexual orientations, while gay or lesbian had the highest impact scores (*F*(`r summary_orientation_effect$Df[1]`, `r summary_orientation_effect$Df[2]`) = `r round(summary_orientation_effect$"F value"[1], 2)`; *p* = `r sprintf("%.3f", summary_orientation_effect$"Pr(>F)"[1])`).
+
 ```{r}
@@
 
-![Sexual Orientation Comparison of Queer Characters' Psychological Impacts](Image/Fig 10_Orientation_Psych_box.png)
+![Sexual Orientation Comparison of Queer Characters' Psychological Impacts](Image/Fig 10_Orientation_Psych_box.png){#fig-plot-orientation-psych-impact}
 
-Racial differences in queer media characters’ psychological impacts were marginally significant (Figure 6).
+ Racial differences in queer media characters’ psychological impacts were marginally significant (@fig-plot-race-psych-impact).
 Specifically, white respondents showed lower psychological impact scores than other racial groups ($M_{\text{white}} = `r round(mean(queer.hypo$psychological_wellbeing_score[queer.hypo$race_category == "White"]), 2)`$ vs.
@@
 Data visualization of bubble plots revealed that queer media exposure frequency and engagement may predict queer media characters’ psychological impacts on LGBTQ+ individuals.
-The bubble plot for queer media exposure and discussion frequency indicated that developed countries have more participants who engaged less with queer media characters, which may contribute to lower impact scores (Figure 7).
+The bubble plot for queer media exposure and discussion frequency indicated that developed countries have more participants who engaged less with queer media characters, which may contribute to lower impact scores (@fig-plot-country-freq).
 Though bubbles for developing countries were smaller, it was the result of a much smaller sample size (*n* = 22) for developing countries' residents than for developed countries' residents (*n* = 145).
-The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (Figure 8), which may contribute to higher community belonging scores and the overall psychological impact scores.
+The bubble plot featuring different gender identities also showed that women, nonbinary, and agender respondents have higher discussion frequency of queer media representations than men (@fig-plot-gender-freq), which may contribute to higher community belonging scores and the overall psychological impact scores.
 
@@
 
-Figure 9 illustrates that the authencity rating positively predicts psychological well-being scores for both developed and developing countries' residents.
+@fig-plot-auth-psych-impact-country illustrates that the authencity rating positively predicts psychological well-being scores for both developed and developing countries' residents.
 The regression line for developing countries' residents is steeper than that for developed countries' residents, indicating that the authenticity rating has a stronger effect on psychological well-being scores for developing countries' residents.
 
-Figure 10 indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities.
+@fig-plot-auth-psych-impact-gender indicates that the authenticity rating positively predicts psychological well-being scores for all gender identities.
 The regression line for men is steeper, indicating that the authenticity rating has a stronger effect on psychological wellbeing scores for men.
@@
 
-Figure 11 illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.
+@fig-plot-auth-psych-impact-orientation illustrates that the authenticity rating positively predicts psychological well-being scores for all sexual orientations.
 It is worth noting that while data points for asexual, gay or lesbian, and pansexual concentrated on the middle to higher end of the authenticity rating and psychological well-being scores, data points for bisexual were more dispersed with much more low score distributions for both ratings.
@@
 
-Figure 12 shows that the authenticity rating positively predicts psychological well-being scores for all racial identities.
+@fig-plot-auth-psych-impact-race shows that the authenticity rating positively predicts psychological well-being scores for all racial identities.
 The regression line for black, asian, and indian respondents is slightly steeper, indicating that racial minorities' perceived psychological impacts by queer characters may be more influenced by the perceived character authenticity than white respondents.
@@
 
-Figure 13 further indicated that queer characters' intersectionality may be a more significant contributor to psychological impact scores for developing countries' residents than for developed countries' residents.
+@fig-plot-inter-psych-impact-country further indicated that queer characters' intersectionality may be a more significant contributor to psychological impact scores for developing countries' residents than for developed countries' residents.
 The regression line for developing countries' residents is steeper, with no intersectionality ratings lower than the middle point.
@@
 
-Though the regressioin line slopes for different gender identities were similar regarding intersectionality rating's effects on psychological impact scores, data points for women and other gender identities were more concentrated on the higher end, with lower intersectionality scores predicting relatively higher psychological impact scores than their men counterparts (Figure 14).
+Though the regressioin line slopes for different gender identities were similar regarding intersectionality rating's effects on psychological impact scores, data points for women and other gender identities were more concentrated on the higher end, with lower intersectionality scores predicting relatively higher psychological impact scores than their men counterparts (@fig-plot-inter-psych-impact-gender).
 Men respondents featured more low psychological impact data points even when the intersectionality rating was high.
@@
 
-Based on the finding that intersectionality rating contributed to higher psychological impact scores for women and other gender identities, Figure 15 compared both gender identity and sexual orientation on differences in intersectionality rating's prediction of psychological impact scores.
+Based on the finding that intersectionality rating contributed to higher psychological impact scores for women and other gender identities, @fig-plot-inter-psych-impact-orientation-gender compared both gender identity and sexual orientation on differences in intersectionality rating's prediction of psychological impact scores.
 The results indicated that intersectionality rating was a stronger predictor of psychological impact scores for bisexual men compared with bisexual women and other gender identities, with a steeper regression line.
@@
 
-Figure 16 illustrates that the intersectionality rating positively predicts psychological well-being scores for all racial identities.
+@fig-plot-inter-psych-impact-race illustrates that the intersectionality rating positively predicts psychological well-being scores for all racial identities.
 The regression line for black, asian, and indian respondents is steeper with more data points concentrated on the higher end of the intersectionality rating and psychological impact scores.

### 2025-02-18 Queer Characters and LGBTQ+ Well-being.qmd
Dingning Yang - Project submission #2 for grading - @nrdowling @Regenchen

@@
   apaquarto-pdf:
-    csl: apa.csl
     documentmode: man
@@
 if(!require(ggplot2)){install.packages("ggplot2")}
+if(!require(ggiraph)){install.packages("ggiraph")}
+if(!require(RColorBrewer)){install.packages("RColorBrewer")}
+if(!require(viridis)){install.packages("viridis")}
+if(!require(maps)){install.packages("maps")}
+if(!require(mapdata)){install.packages("mapdata")}
+if(!require(gridExtra)){install.packages("gridExtra")}
+if(!require(plotly)){install.packages("plotly")}
+if(!require(wordcloud2)){install.packages("wordcloud2")}
+if(!require(shiny)){install.packages("shiny")}
 if(!require(psych)){install.packages("psych")}
@@
 # List of required packages
-required_packages <- c ("tidyverse", "ggplot2", "psych","knitr", "kableExtra")
+required_packages <- c ("tidyverse", "ggplot2", "ggiraph", "RColorBrewer", "viridis", "maps", "mapdata","gridExtra", "plotly", "wordcloud2", "shiny", "psych","knitr", "kableExtra")
 
